\documentclass[defaultstyle,11pt]{thesis}

\usepackage{amssymb}		% to get all AMS symbols
\usepackage{graphicx}		% to insert figures
\usepackage{hyperref}		% PDF hyperreferences??
\usepackage{listings}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{blindtext}
\usepackage{siunitx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{float}
\usepackage{multirow}


\newtheorem{definition}{Definition}
\newtheorem{theorem}[definition]{Theorem}

%%%%%%%%%%%%   All the preamble material:   %%%%%%%%%%%%

\title{Proximity-informed robot control through whole-body artificial skin}

\author{A.}{Aranburu Fernández}

\otherdegrees{B.A., UPV/EHU Euskal Herriko Unibertsitatea, 2017 \\
			  M.S., UPC Universitat Politecnica de Catalunya, 2020}

\degree{Master of Science}		%  #1 {long descr.}
	{M.S., Industrial Engineering}		%  #2 {short descr.}

\dept{Department of}			%  #1 {designation}
	{Computer Science}		%  #2 {name}

\advisor{Prof.}				%  #1 {title}
	{Alessandro Roncone}			%  #2 {name}

%\reader{Caleb Escobedo}		%  2nd person to sign thesis

\abstract{ % \OnePageChapter	% because it is very short

Human-Robot Interaction is the field of robotics dedicated to the understanding, design, and evaluation of robotic systems for use by or with humans. Safety is one of the most important aspects this field will have to deal with in the years to come. In this work, pre-contact safety is adressed through the use of an artificial skin developed in our lab that integrates proximiy sensing. Proximity sensor readings are transformed into 3D data, which will later inform the control algorithms. Two different avoidance controls have been implemented: ``A Depth Space Approach to Human-Robot Collision Avoidance'' \cite{flacco2012depth} and ``Collision Avoidance with Proximity Servoing for Redundant Serial Robot Manipulators'' \cite{dingcollision}. The implementations of these two controllers form, with the addition of a third controller that improves upon both of them, a framework for the comparison and improvement of the current state of art in safe robot controllers.

	}

% \dedication[Dedication]{	% NEVER use \OnePageChapter here.
% 	To all of the fluffy kitties.
% 	}

\acknowledgements{	\OnePageChapter	% *MUST* BE ONLY ONE PAGE!
    I would like to acknowledge everyone that played an important role in the completion of my master's degree and this master Thesis. First of all, my parents, without whom nothing I have accomplished woud have ever been possible.

    Secondly, my supervisor Prof. Alessandro Roncone, thank you for giving me the opportunity to work in HIRO and for the patient guidance, encouragement and advice.

    Finally, I must also express my gratitude to my workmate Caleb Escobedo and all of the members of the lab. Thank you for helping me throughout my stay in the United States and for sharing your knowledge.
	}

% \IRBprotocol{E927F29.001X}	% optional!

\ToCisShort	% use this only for 1-page Table of Contents

% \LoFisShort	% use this only for 1-page Table of Figures
\emptyLoF	% use this if there is no List of Figures

% \LoTisShort	% use this only for 1-page Table of Tables
\emptyLoT	% use this if there is no List of Tables

% Set C++ Code format
\lstset
{
    language=C++,
    keywordstyle=\color{blue},
    stringstyle=\color{red},
    commentstyle=\color{green},
    morecomment=[l][\color{magenta}]{\#},
    basicstyle=\linespread{0.95}\ttfamily,
    frame=top,
	frame=bottom,
	% frame=left,
	% frame=right,
    escapeinside={(*}{*)},
    numbers=right,
    % breaklines=true,
    aboveskip=1.5em,
	% belowskip=1em,
	% backgroundcolor=\color{lightgray},
}

\lstloadlanguages{ % Check documentation for further languages ...
     % [Visual]Basic,
     % Pascal,
     % C,
     C++,
     % XML,
     % HTML,
	%  Java,
	Python
}
\newcounter{codecounter}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%       BEGIN DOCUMENT...         %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\input macros.tex
\input chapter1.tex
\input chapter2.tex
\input chapter3.tex
\input chapter4.tex
\input chapter5.tex
% \input example_chapter1.tex
% \input example_chapter2.tex

%%%%%%%%%   then the Bibliography, if any   %%%%%%%%%
\bibliographystyle{unsrt}	% or "plain" "siam", or "alpha", etc.
\nocite{*}		% list all refs in database, cited or not
\bibliography{refs}		% Bib database in "refs.bib"

%%%%%%%%%   then the Appendices, if any   %%%%%%%%%
% \appendix

% \input example_appendixA.tex
% \input example_appendixB.tex


\end{document}
